Roster Review (Generic)

### 2019-06-04 rosterReview_generic.Rmd
Some WAR draft views

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Deez",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Deez",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters %>% 
  filter(grepl("Dorn|Plouffe",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Puig|Yonny Chir",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

@@

```{r}
#TODO measuring projected value of draft picks, move to separate research
rosters %>% 
  filter(!is.na(draft_pick)) %>%
  group_by(draft_round) %>% 
  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=zar_mean)) +
  geom_col() +
  geom_line(aes(y=zar_median)) -> draft_plot

@@

rosters %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  arrange(draft_round) %>% 
  ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
  geom_boxplot()
```

>>>>

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Dorn",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Dorn",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters %>% 
  filter(grepl("Dorn|process",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Trout|Whitley|Cain|Price",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))

rosters %>% 
  filter(grepl("Dorn|process",team)) %>% 
  select(team, manager, name_full, display_position, war) %>% 
  filter(grepl("Trout|Whitley|Cain|Price",name_full))
```

@@

```{r}
#TODO measuring projected value of draft picks, move to separate research
#TODO get beginning of year zar/war values
rosters %>% 
  filter(!is.na(draft_pick)) %>%
  group_by(draft_round) %>% 
  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=zar_mean)) +
  geom_col() +
  geom_line(aes(y=zar_median)) -> draft_plot

@@

rosters %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  arrange(draft_round) %>% 
  ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
  geom_boxplot()

rosters %>% 
  filter(!is.na(draft_pick)) %>%
  group_by(draft_round) %>% 
  summarize(war_median = median(war) %>% janitor::round_half_up(),
            war_mean = mean(war) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=war_mean)) +
  geom_col() +
  geom_line(aes(y=war_median)) -> draft_plot_war

ggplotly(draft_plot_war)

rosters %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  arrange(draft_round) %>% 
  ggplot(aes(x=draft_round,y=war,group=draft_round)) +
  geom_boxplot()
```
